\textbf{Instructor's Note}

PS2 requires more coding than PS1 and training multiple models. It is important that you
start this assignment early! It is also in your best interest to make sure that your code 
is properly vectorized (at no point in this assignment do you need to implement a for-loop) 
so that the models run faster. If you plan on training the models on GPU, make sure your 
code can also run on CPU since this we will be running the autograder on CPU. 
Also, if your GPU has limited memory ($\le$ 2 GB), you will likely run into Out-of-Memory issues on Problem 3.

Here are the expected train times for each part of the assignment:
\begin{enumerate}
    \item ~7 minutes for \texttt{vae.py}
    \item ~7 minutes for \texttt{gmvae.py}
    \item ~50 minutes for \texttt{ssvae.py}
    \item $\ge$ 3 hours for \texttt{fsvae.py}. We recommend stopping training the moment your samples
    look somewhat decent (maybe around 50000 iterations). Note that we periodically
    save models for you.
\end{enumerate}

The following is a checklist of various functions you need to implement in the
submission, in chronological order:

\begin{enumerate}
    \item \texttt{sample\_gaussian} in \texttt{src/submission/utils.py}
    \item \texttt{negative\_elbo\_bound} in \texttt{src/submission/models/vae.py}
    \item \texttt{log\_normal} in \texttt{src/submission/utils.py}
    \item \texttt{log\_normal\_mixture} in \texttt{src/submission/utils.py}
    \item \texttt{negative\_elbo\_bound} in \texttt{src/submission/models/gmvae.py}
    \item \texttt{negative\_iwae\_bound} in \texttt{src/submission/models/vae.py}
    \item \texttt{negative\_iwae\_bound} in \texttt{src/submission/models/gmvae.py}
    \item \texttt{negative\_elbo\_bound} in \texttt{src/submission/models/ssvae.py}
    \item \bf{Extra Credit}: \texttt{negative\_elbo\_bound} in \texttt{src/submission/models/fsvae.py}
\end{enumerate}

You will submit the entire \texttt{submission} directory. To do so run the command  below from the \texttt{src} directory
\begin{verbatim}
    bash collect_submission.sh
\end{verbatim}

or you can choose to zip the folder up manually.
